---
title: "Exercise: Explore, Clean, and Wrangle Data"
author: "Daya Muralidharan"
format: html
---

## About the data
This data is collected along the mainland coast of the Santa Barbara Channel on the California spiny lobster. This dataset contains 2 tables - abundance & size data and fishing pressure. Sampling began in 2012 and is ongoing. This data was retrieved on June 29, 2023 from this [link](https://portal.edirepository.org/nis/mapbrowse?packageid=knb-lter-sbc.77.8) 

## Setup

Loading the libraries
```{r}
library(readr)
library(dplyr)
library(ggplot2)
library(tidyr)
```


## Read and explore data

```{r}
lobster_abundance <- read_csv("https://portal.edirepository.org/nis/dataviewer?packageid=knb-lter-sbc.77.8&entityid=f32823fba432f58f66c06b589b7efac6")

lobster_traps <- read_csv("https://portal.edirepository.org/nis/dataviewer?packageid=knb-lter-sbc.77.8&entityid=66dd61c75bda17c23a3bce458c56ed84")
```
```{r}
summary(lobster_abundance)
```

```{r}
summary(lobster_traps)
```


## Exercise 1

## Exercise 2

## Exercise 3

## Exercise 4

## Exercise 5

## Exercise 6